How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985

### 2022-09-22 Draft_September_2022/Full_draft_20220901.rmd
Updated the last regression table with odds ratio and confidence intervals

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(sjPlot)
library(parameters)

Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r Table 3, eval=FALSE, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE, results="asis"}

tab_model(model_logit_con2,model_logit_ei2,model_logit_sd2,model_logit_sov2)

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(modelsummary)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r Table 3, fig.cap="Odds Ratio and Confidence Intervals", message=FALSE, warning=FALSE, echo=FALSE, paged.print=TRUE, include=TRUE}

modelsummary::modelsummary(list("Conservation" = model_logit_con2,
                                "Economic Integration" = model_logit_ei2,
                                "Social Development" = model_logit_sd2,
                                "Sovereignty" = model_logit_sov2),
                           title = "Odds Ratio and Confidence Intervals",
                           exponentiate = TRUE, statistic = "conf.int")
